Automatic discovery of cell types and microcircuitry from neural connectomics

### 2014-06-17 docs/paper.tex
updates to paper text

\documentclass{nature}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsmath}
%\usepackage{subcaption}
%\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics{comparison.ai}}
  \caption{Comparison of the value of incorporating additional metadata 
for the mouse retina connectome.}
\label{fig:mouseretina_compare}
\end{figure}

@@

\begin{itemize}
\item \textbf{synthetic}: For synthetic datasets of sizes comparable to our
real data size, do we recover known ground truth information
after running our markov chains for the appropriate amount of time? 
\todo{Add figure}
\item \textbf{autocorrelation} For various summary statistics 
of the latent space, after a certain amount of time 
\todo{add figure}
\end{itemize}

@@

>>>>

%\documentclass{nature}
\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsmath}
%\usepackage{subcaption}
%\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

\begin{figure}
  \centering 
  \centerline{\includegraphics{comparison.ai}}
  \caption{a. Cell-cell assignment matrix reflecting the posterior distribution of clusterings found by our model. Large contiguous black areas are cells that were considered the same type in the majority of samples. b. The cells and their true types sorted to agree with the coassignment matrix. c. A comparison of the predictive accuracy (Area under the curve) for hand-labeled anatomical data, versus inclusion of additional sources of information. d. ) The spatial extent (in depth and area) of the types identified by humans and our various algorithmic approaches.}

\label{fig:mouseretina_compare}
\end{figure}

@@

\begin{itemize}
\item \textbf{synthetic}: For synthetic datasets of sizes comparable to our
real data size, do we recover known ground truth information
after running our markov chains for the appropriate amount of time? 
\todo{Add figure}
\item \textbf{autocorrelation} For various summary statistics 
of the latent space, after a certain amount of time

\end{itemize}

@@

\todo{Concerns about parameter sensitivity}
\todo{How did we pick the best one we often show?}
